---
title: "Determinants of NBA Players' Salary"
author: "Albert L Hu, Sarah Hu, Ming Ho Cheung, Zihan Chen"
date: "December 2, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction {.flexbox .vcenter}

In the 2013-2014 National Basketball Association (NBA) season, the Los Angeles Laker’s Kobe Bryant earned $30.4 million whereas the average NBA player salary is about 5 million. Is Kobe that much better than a player who earns 5 millions a year? Thus the question whether NBA players are overpaid arises.

Our project serves to highlight the performance variables, such as points, turnovers, and blocks, that affect players’ salary in NBA. The methodology is chosen as not only closely analyze performance of players, but as a further motivation in seeking 

## Analytical and Motivating Question {.flexbox .vcenter}

What are the determinants of NBA players' salary?

How the skills of a player is related to his salary?

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
str(roster_salary_stats)
```

## Slide with Plot

```{r pressure}

```

